Assessment of the KLGO Coastal Waterbird Survey Monitoring Program

### 2019-02-06 analysis/paper/paper.Rmd
Corrected relative paths to source'd files (and removed temporary code used in debugging)

#NOTE: working directory when knitting markup is /analysis/paper. So relative pathway needs to be ../scripts etc.
print(getwd())
#source("./analysis/scripts/data_retrievalCSV.R")
source("../scripts/data_retrievalCSV.R") #JR added 2019 Feb 5, need '..' to reference relative parent directory.

@@

```{r, eval=TRUE}
#source("./analysis/scripts/data_exploration.R")
source("../scripts/data_exploration.R") # JR 2019 Feb 5 corrected relative pathname

#source("../scripts/units_species.R")
```

>>>>

#NOTE: working directory when knitting markup is /analysis/paper. So relative pathway needs to be ../scripts etc.
source("../scripts/data_retrievalCSV.R")

@@

```{r, eval=TRUE}
source("../scripts/data_exploration.R") 
```
